---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)

library(table.glue)
library(tidyverse)
library(gt)

```

# rfvs-regression

<!-- badges: start -->
<!-- badges: end -->

The goal of rfvs-regression is to compare random forest variable selection techniques for continuous outcomes

# Datasets included

```{r}

tbl <- read_csv("data/datasets_inclusion_chart.csv", 
         show_col_types = FALSE) %>% 
 gt(rowname_col = 'exclusion') %>% 
 tab_footnote(locations = cells_stub(rows = 8), 
              footnote = 'Many datasets are different versions of the same data')

gtsave(tbl, filename = 'doc/gt_readme_1.png')

magick::image_read("doc/gt_readme_1.png")

```

# Central illustration

The experiment we ran involves three steps:

1. Select variables with a given method.
1. Fit a random forest to the data, including only selected variables.
1. Evaluate prediction accuracy of the forest in held-out data.

*Note*: We use both axis-based and oblique random forests for regression in step 2. 

We assume that better variable selection leads to better prediction accuracy. Results from the experiment are below.

```{r}

targets::tar_load(results_smry)


data_tbl <- results_smry$overall %>% 
 ungroup() %>% 
 mutate(
  rfvs = str_remove(rfvs, 'rfvs_'),
  across(starts_with('n_selected'), ~ as.integer(round(.x))),
  across(starts_with('time'),  ~ as.numeric(.x, units = 'secs'))
 ) %>% 
 arrange(rsq_axis_50)

tbl_vars <- c('n_selected',
              'rsq_oblique', 
              'rsq_axis',
              'time')

for(t in tbl_vars){
 
 t25 <- data_tbl[[paste(t, "25", sep = '_')]]
 t50 <- data_tbl[[paste(t, "50", sep = '_')]]
 t75 <- data_tbl[[paste(t, "75", sep = '_')]]
 
 data_tbl[[t]] <- table_glue("{t50} ({t25} - {t75})")
 
}

tbl <- data_tbl %>% 
 arrange(n_selected_50) %>% 
 select(rfvs, all_of(tbl_vars)) %>% 
 gt(rowname_col = 'rfvs', caption = "Table values present the median (25th percentile, 75th percentile).") %>% 
 tab_stubhead("Variable selection method") %>% 
 cols_label(n_selected = 'N variables selected',
            rsq_oblique = 'Oblique',
            rsq_axis = 'Axis-based',
            time = 'Selection time, seconds') %>% 
 tab_spanner(columns = c("rsq_oblique", "rsq_axis"), 
             label = "R-squared") %>% 
 cols_align('center') %>% 
 cols_align('left', columns = 'rfvs')

gtsave(tbl, filename = 'doc/gt_readme_2.png')

magick::image_read("doc/gt_readme_2.png")

```


Similar results, but using mean and standard error

```{r}

data_tbl <- results_smry$overall %>% 
 ungroup() %>% 
 mutate(
  rfvs = str_remove(rfvs, 'rfvs_'),
  across(starts_with('time'),  ~ as.numeric(.x, units = 'secs'))
 ) %>% 
 arrange(rsq_axis_mean)

tbl_vars <- c('n_selected',
              'rsq_oblique', 
              'rsq_axis',
              'time')

for(t in tbl_vars){
 
 .m <- data_tbl[[paste(t, "mean", sep = '_')]]
 .se <- data_tbl[[paste(t, "se", sep = '_')]]
 
 data_tbl[[t]] <- table_glue("{.m} ({.se})")
 
}

tbl <- data_tbl %>% 
 arrange(n_selected_mean) %>% 
 select(rfvs, all_of(tbl_vars)) %>% 
 gt(rowname_col = 'rfvs', caption = "Table values are mean (standard error).") %>% 
 tab_stubhead("Variable selection method") %>% 
 cols_label(n_selected = 'N variables selected',
            rsq_oblique = 'Oblique',
            rsq_axis = 'Axis-based',
            time = 'Selection time, seconds') %>% 
 tab_spanner(columns = c("rsq_oblique", "rsq_axis"), 
             label = "R-Squared") %>% 
 cols_align('center') %>% 
 cols_align('left', columns = 'rfvs')

gtsave(tbl, filename = 'doc/gt_readme_3.png')

magick::image_read("doc/gt_readme_3.png")

```


```{r}

meta <- data.table::fread("data/datasets_included.csv") %>% 
 transmute(dataset = name, 
           n_obs = number.of.instances,
           p_uni = n_uni / n_obs, 
           n_col = number.of.features, 
           p_col_catg = number.of.symbolic.features / n_col,
           p_col_ctns = number.of.numeric.features / n_col,
           p_miss = miss_prop)

targets::tar_load(bm_comb)

data_model <- left_join(bm_comb, meta) %>% 
 select(-outcome, -run, -n_selected, -starts_with("rmse"))

# library(lme4)
# library(lmerTest)
# 
# fit <- lmerTest::lmer(rsq_oblique ~ 0 + rfvs*log(n_obs) + (1|dataset), 
#                       data = data_model)
# 
# summary(fit)
# 
# anova(fit)

data_model %>% 
 mutate(time = as.numeric(time, units = 'secs')) %>% 
 filter(rfvs != "none") %>% 
 mutate(rfvs = fct_reorder(rfvs, .x = time, .fun = median)) %>% 
 ggplot() + 
 aes(x = rfvs, y = time) + 
 geom_boxplot() + 
 scale_y_log10() + 
 labs(y = "time to select variables, seconds",
      title = 'Computational efficiency of variable selection methods')

```



```{r}

data_model %>%
 pivot_longer(starts_with("rsq")) %>% 
 mutate(rfvs = fct_reorder(rfvs, .x = value, .fun = median)) %>% 
 ggplot() + 
 aes(x = rfvs, y = value, fill = name) + 
 geom_boxplot(outlier.shape = NA) + 
 scale_y_continuous(limits = c(0,1)) +
 labs(y = "R-squared of downstream model",
      title = 'Prediction accuracy based on variable selection methods')

```

